Linearizability Proofs Based On Forward Simulations

### 2017-01-17 draftCAV/queue.tex
simulation for HW
small modif

We describe a forward simulation $\mathit{fs}$ from $\mathit{HWQ}$ to $AbsQ$. Essentially, an $AbsQ$ state associated by $\mathit{fs}$ to a $\mathit{HWQ}$ state consists of all the  enqueue operations for which the input is still present in the array {\tt items} and all the pending enqueue operations that have at most reserved an array position, ordered by a relation $<$ satisfying the following: 
\begin{itemize}
	\item[(a)] pending enqueues are maximal, i.e., for every two enqueues $k$ and $k'$ such that $k'$ is pending, we have that $k'\not< k$,
	\item[(b)] $<$ is consistent with the order in which positions of {\tt items} have been reserved, i.e., for every two enqueues $k$ and $k'$ such that ${\tt i}(k) < {\tt i}(k')$, we have that $k' \not< k$,
	\item[(c)] an enqueue which has reserved an array position $i$ %and executed only the first statement 
	can't be ordered before another enqueue that has reserved a position $j > i$ when the position $i$ has been ``observed'' by a non-linearized dequeue that may ``observe'' $j$ in the current array traversal (we also require that the dequeue has just finished the execution of {\tt swap}), i.e., for every two enqueues $k$ and $k'$, and a dequeue $k_d$, such that

@@

>>>>

We describe a forward simulation $\mathit{fs}$ from $\mathit{HWQ}$ to $AbsQ$. Essentially, an $AbsQ$ state associated by $\mathit{fs}$ to a $\mathit{HWQ}$ state consists of all the  enqueue operations for which the input is still present in the array {\tt items} and all the pending enqueue operations that have at most reserved an array position, ordered by a relation $<$ satisfying the following: 
\begin{itemize}
	\item[(a)] pending enqueues are maximal, i.e., for every two enqueues $k$ and $k'$ such that $k'$ is pending, we have that $k'\not< k$,
	\item[(b)] $<$ is consistent with the order in which positions of {\tt items} have been reserved, i.e., for every two enqueues $k$ and $k'$ such that ${\tt i}(k) < {\tt i}(k')$, we have that $k' \not< k$,
	\item[(c)] an enqueue which has reserved an array position $i$ %and executed only the first statement 
	can't be ordered before another enqueue that has reserved a position $j > i$ when the position $i$ has been ``observed'' by a non-linearized dequeue that may ``observe'' $j$ in the current array traversal, i.e., for every two enqueues $k$ and $k'$, and a dequeue $k_d$, such that

@@

TODO LINEARIZATION POINT
